`flippant` --- An `R` package for the automated analysis of dithionite scramblase

### 2016-07-19 inst/manuscript/manuscript.rmd
tmpDir -> analysis_dir for clarity

tmpDir <- tempdir()
file.path("extdata", "PloierEtAl_Data.zip") %>%
  system.file(
    package = "flippant",
    mustWork = TRUE) %>%
  unzip(
    overwrite = TRUE,
    exdir = tmpDir)

@@

```{r noeval_demonstrate_traces, eval = FALSE}
template_file <- "extdata/PloierEtAl_Data.zip" %>% 
  system.file(package = "flippant") %>% 
  unzip(files = "inputTable.txt")
# Plot spectral traces (Figure 1)
scramblase_assay_traces(
  template_file,
  time_max_sec = 350)
```

@@

```{r figure1_creation, echo = FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
# Plot spectral traces (Figure 1)
x <- tmpDir %>%
  file.path(template_file) %>%
  flippant:::read_scramblase_input_file()
x[["Path"]] <- file.path(tmpDir, x[["Path"]])
flippant::scramblase_assay_traces(
  x,
  time_max_sec = 350)
```

>>>>

analysis_dir <- tempdir()
file.path("extdata", "PloierEtAl_Data.zip") %>%
  system.file(
    package = "flippant",
    mustWork = TRUE) %>%
  unzip(
    overwrite = TRUE,
    exdir = analysis_dir)

@@

```{r noeval_demonstrate_traces, eval = FALSE}
analysis_dir <- tempdir()
template_file <- "extdata/PloierEtAl_Data.zip" %>% 
  system.file(package = "flippant") %>% 
  unzip(files = "inputTable.txt", exdir = analysis_dir)

# Plot spectral traces (Figure 1)
scramblase_assay_traces(
  template_file,
  time_max_sec = 350)
```

@@

```{r figure1_creation, echo = FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
# Plot spectral traces (Figure 1)
x <- analysis_dir %>%
  file.path(template_file) %>%
  flippant:::read_scramblase_input_file()
x[["Path"]] <- file.path(analysis_dir, x[["Path"]])
flippant::scramblase_assay_traces(
  x,
  time_max_sec = 350)
```
